\href{http://www.sigcomm.org/content/ebook}{Recent Advances in Networking}

### 2013-08-07 Compiled/ebook.tex
added last page
added page numbers and fixed acents in intro

\author{
\href{http://www.eecs.qmul.ac.uk/~hamed/}{Hamed Haddadi},  \href{http://www.uclouvain.be/olivier.bonaventure}{Olivier Bonaventure} (Editors)\\
\\
\\
\href{http://www.sigcomm.org/}{ACM SIGCOMM}
}

@@

\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter7/chapter7.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter5/chapter5.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter8/chapter8.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter2/chapter2.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter3/chapter3.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter6/chapter6.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter4/paper.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter1/chapter1.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter9/chapter9.pdf}

@@

>>>>

\author{
\href{http://www.eecs.qmul.ac.uk/~hamed/}{Hamed Haddadi},  \href{http://perso.uclouvain.be/olivier.bonaventure}{Olivier Bonaventure} (Editors)\\
\\
\\
\href{http://www.sigcomm.org/}{ACM SIGCOMM}
}

@@

\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter7/chapter7.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter5/chapter5.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter8/chapter8.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter2/chapter2.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter3/chapter3.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter6/chapter6.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter4/chapter4.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter1/chapter1.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter9/chapter9.pdf}

@@

\input{intro/lastpage.tex}

### 2013-08-07 Compiled/intro/board.tex
fixes
added page numbers and fixed acents in intro

\Large 
\vspace{1in}
\begin{tabular}{ll}
Ernst Biersack &	Eurecom \\
Olivier Bonaventure &	Universit$\acute{e}$ catholique de Louvain \\
Jon Crowcroft	&  University of Cambridge \\
Walid Dabbous	  & INRIA Sophia Antipolis \\
Bruce Davie	& VMware \\
Anja Feldmann	& Technische Universit$\ddot{a}$t Berlin\\
Timothy Griffin	& University of Cambridge \\
Hamed Haddadi &	Queen Mary University of London\\
Ramesh Johari	 & Stanford University\\
Srinivasan Keshav &	University of Waterloo\\
Jean-Yves Le Boudec	& $\acute{E}$cole polytechnique F$\acute{e}$d$\acute{e}$rale de Lausanne\\
Jennifer Rexford &	Princeton University\\
David Wetherall	& University of Washington\\
Walter Willinger	& AT\&T Labs Research\\
\end{tabular}
\end{center}

@@

\begin{center}
{\Huge \textbf{Review Board}}

\Large 
\vspace{1in}

\begin{tabular}{ll}
Mark Allman &	International Computer Science Institute \\
Emmanuel Baccelli    &	INRIA Saclay\\
Saleem Bhatti	& University of St Andrews \\
Olivier Bonaventure &	Universit$\acute{e}$ catholique de Louvain \\
Gonzalo Camarillo  &  Ericsson Research   \\
Dah Ming Chiu   &   The Chinese University of Hong Kong \\
Costas Courcoubetis  & Athens University of Economics and Business \\
Mark Crovella & Boston University \\
Jon Crowcroft	&  University of Cambridge \\
Bruce Davie	& VMware \\
Benoit Donnet  &   Universit$\acute{e}$ de Li$\grave{e}$ge  \\
Damien Fay & Bournemouth University  \\
Paul Francis & Max Planck Institute for Software Systems \\
Hamed Haddadi &	Queen Mary University of London\\
Luigi Iannone &  TELECOM ParisTech \\
Srinivasan Keshav    &	University of Waterloo\\
Olaf Maennel  & Loughborough University \\
Konstantinos Nikitopoulos & University College London \\
Costin Raiciu &  Universitatea Politehnica Bucuresti  \\
Jennifer Rexford &	Princeton University\\
Miguel Rio & University College London \\ 
Matthew Roughan & University of Adelaide \\
Jean-Louis Rougier  &  TELECOM ParisTech \\
Damien Saucez  & INRIA Sophia Antipolis \\
Aman Shaikh  & AT\&T Labs Research \\
Steve Uhlig & Queen Mary University of London\\
\end{tabular}
\end{center}

>>>>

\Large 
\vspace{1in}
\begin{tabular}{ll}
Ernst Biersack &	Eurecom \\
Olivier Bonaventure &	Universit\'{e} catholique de Louvain \\
Jon Crowcroft	&  University of Cambridge \\
Walid Dabbous	  & INRIA Sophia Antipolis \\
Bruce Davie	& VMware \\
Anja Feldmann	& Technische Universit\"{a}t Berlin\\
Timothy Griffin	& University of Cambridge \\
Hamed Haddadi &	Queen Mary University of London\\
Ramesh Johari	 & Stanford University\\
Srinivasan Keshav &	University of Waterloo\\
Jean-Yves Le Boudec	& \'{E}cole polytechnique F\'{e}d\'{e}rale de Lausanne\\
Jennifer Rexford &	Princeton University\\
David Wetherall	& University of Washington\\
Walter Willinger	& AT\&T Labs Research\\
\end{tabular}
\end{center}

@@

\begin{center}
{\Large \textbf{Review Board}}

\vspace{1in}

\begin{tabular}{ll}
Mark Allman &	International Computer Science Institute \\
Emmanuel Baccelli    &	INRIA Saclay\\
Saleem Bhatti	& University of St Andrews \\
Olivier Bonaventure &	Universit\'{e} catholique de Louvain \\
Gonzalo Camarillo  &  Ericsson Research   \\
Dah Ming Chiu   &   The Chinese University of Hong Kong \\
Costas Courcoubetis  & Athens University of Economics and Business \\
Mark Crovella & Boston University \\
Jon Crowcroft	&  University of Cambridge \\
Bruce Davie	& VMware \\
Benoit Donnet  &   Universit\'{e} de Li\`{e}ge  \\
Damien Fay & Bournemouth University  \\
Paul Francis & Max Planck Institute for Software Systems \\
Hamed Haddadi &	Queen Mary University of London\\
Luigi Iannone &  TELECOM ParisTech \\
Srinivasan Keshav    &	University of Waterloo\\
Olaf Maennel  & Loughborough University \\
Konstantinos Nikitopoulos & University College London \\
Costin Raiciu &  Universitatea Politehnica Bucuresti  \\
Jennifer Rexford &	Princeton University\\
Miguel Rio & University College London \\ 
Matthew Roughan & University of Adelaide \\
Jean-Louis Rougier  &  TELECOM ParisTech \\
Damien Saucez  & INRIA Sophia Antipolis \\
Aman Shaikh  & AT\&T Labs Research \\
Steve Uhlig & Queen Mary University of London\\
\end{tabular}
\end{center}
